GVN-Hoist: Hoisting Computations from Branches

### 2016-08-18 hoist.tex
results on llvm-testsuite

\section{Experimental Evaluation}
\label{sec:experimental-results}

>>>>

\section{Experimental Evaluation}
\label{sec:experimental-results}
We ran llvm-testsuite (trunk:d87471f8) with the patch (trunk:86940146 and the results are:

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|c|}
      \hline
      Metric                   	     & Number\\\hline
      Instructions hoisted & 21616 \\\hline
      Instructions removed & 30438 \\\hline
      Loads hoisted        & 14802 \\\hline
      Loads removed        & 20719 \\\hline
      Stores hoisted       & 15    \\\hline
      Stores removed       & 15    \\\hline
      Calls hoisted        & 8     \\\hline
      Calls removed        & 8     \\\hline
\end{tabular}
  \end{center}
  \caption{Code hoisting metrics on llvm-testsuite}
  \label{tab:results}
\end{table}
